Technical Report

### 2024-02-19 Reports/tech_report1.tex
update report

This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new hyperplane constraints.

@@

This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new hyperplane constraints.

@@

@@

>>>>

This experiment is to find the best open ReLU number for layer 5 normal 5x100 with new hyperplane constraints. In addition, this test also compute the gamma data for layer 3 based on previous found best open number.

@@

This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new hyperplane constraints. In addition, this test also compute the gamma data for layer 5 based on previous found best open number.

@@

\begin{itemize}
	\item\emph{Experiments Id}: 021700102024

@@

\subsection{Randomly choose open ReLU for layer 3 for normal 5x100}

This experiment is to test the random open ReLU nodes for layer 3 normal 5x100 with new hyperplane constraints.

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py| (a copy for it is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_random.py|). And the partial output file name is \verb*|Gamma_5x100_normal_layer3_seek_openrelu_random.txt|.  It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 3 with different open ReLU numbers and nodes chosen randomly.

	\item\emph{Open $\ReLU$ number:} Open 15,18,21,24,27 ReLU nodes for each node, but choose open nodes randomly.

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer3_seek_openrelu_random.txt|

	\item \emph{Total time:} 14072.

	\item \emph{Key results:} $\gamma$ for different open number are 0.28773090140361735,
	0.2804030901915068,
	0.2733447337312936,
	0.26386494446982417,
	0.2613191792848188. This is much worse than open node by our method.

\end{itemize}
